AGEAS: Automated Machine Learning based Genetic Regulatory Element Extraction System

### 2022-10-09 docs/manuscript/main.tex
v0.0.1a9
Minor stuffs

\section*{Introduction}
  \label{introduction}
  As high-resolution sequencing technologies become increasingly applicable and accessible, an efficient and robost analytical system capable of extracting key genetic features responsible for cell types and cell states difference with limited prior biological knowledge also become highly demanded.
  Several methodologies like SCENIC \cite{Scenic} already demonstrated informativeness and robustness in studying cellular phenotypes with GRN analysis.
  Regulons, collections of a TF and corresponding targetomes, can successfully address cell identities with more comprehensive information compared with differential expressing genes (DEGs). \cite{Scenic, pySCENIC}
  Even though limited computational methods are capable to completely and precisly extract key genetic regulatory elements in biological process of interest, Mogrify\cite{mogrify_2016} and CellNet\cite{cellnet_2014} have demonstrated GRN based methods can help to analysis cell type differentiation and implement cell reprogramming.
  However, either method may require large scale of additional background data to be applicable in other studies such as analyzing physiological or pathological development of selected cell type.
  The scREMOTE \cite{scREMOTE} published in 2022 shows great potential as generalized regulatory element extraction method since limited background data is required with sequencing data representing sample classes.
  But prior knowledge on key TFs and marker genes is still indispensable.
  Indeed, a regulation trajectory of DEGs or regulons showing significant activity difference after GRN reconstruction would be able to reveal the developmental pathways as generalized approach, but numerous noisy signals are expected due to general gene regulatory nature of TFs.
  Therefore, here we present AGEAS with feasibility in extracting key regulatory elements for biological phenomena of interest even with scarce prior knowledge and potentially promote further experiments.

>>>>

\section*{Introduction}
  \label{introduction}
  As high-resolution sequencing technologies become increasingly applicable and accessible, an efficient and robost analytical system capable of extracting key genetic features responsible for cell types and cell states difference with limited prior biological knowledge also become highly demanded.
  Several methodologies like SCENIC \cite{Scenic} already demonstrated informativeness and robustness in studying cellular phenotypes with GRN analysis.
  Regulons, collections of a TF and corresponding targetomes, can successfully address cell identities with more comprehensive information compared with differential expressing genes (DEGs). \cite{Scenic, pySCENIC}
  Even though limited computational methods are capable to completely and precisly extract key genetic regulatory elements in biological process of interest, Mogrify\cite{mogrify_2016} and CellNet\cite{cellnet_2014} have demonstrated GRN based methods can help to analysis cell type differentiation and implement cell reprogramming.
  However, either method may require large scale of additional background data to be applicable in other studies such as analyzing physiological or pathological development of selected cell type.
  The scREMOTE \cite{scREMOTE} published in 2022 shows great potential as generalized regulatory element extraction method since limited background data is required with sequencing data representing sample classes.
  But prior knowledge on key TFs and marker genes is still indispensable.
  Indeed, a regulation trajectory of DEGs or regulons showing significant activity difference after GRN reconstruction would be able to reveal the developmental pathways as generalized approach, but numerous noisy signals are expected due to general gene regulatory nature of TFs.
  Therefore, here we present AGEAS with feasibility in extracting key regulatory elements for biological phenomena of interest even with scarce prior knowledge and potentially promoting further discoveries.
